Dark Control:\\ Towards a Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-12-05 paper/paper.tex
Clarification of memory and POMDPs

% , defining $s(t)$, the state at time $t$, as the position in state space.
The process has $memory$ if the next state depends not only on the current state
but also on a finite number of past states.
Rational probabilistic planning can thus be reformulated
as a standard memoryless Markov process by simply expanding the
definition of the state $s$ to include experience episodes of the past.
This adds the capacity for memory, since then, the next state depends not only on the current state but also on a finite number of past states. This is precisely what partially observable MDPs do ~\citep{starkweather2017dopamine,o2006making}.

>>>>

% , defining $s(t)$, the state at time $t$, as the position in state space.
The process has $memory$ if the next state depends not only on the current state
but also on a finite number of past states.
Rational probabilistic planning can thus be reformulated
as a standard memoryless Markov process by simply expanding the
definition of the state $s$ to include experience episodes of the past.
This adds the capacity for memory, since then, the next state depends not only on the current state but also on a finite number of past states. This is precisely what Partially Observable MDPs (POMDPs) do ~\citep{starkweather2017dopamine,o2006making}.
Nevertheless, this mathematical procedure in POMDPs only accounts for implicit $memory$. Since the current paper is aiming at both plausibility at the behavioral and neural level, we will address later in the paper how our model captures the neurophysiological constraints of the DMN and can also account for the explicit part of $memory$ from a human agent perspective.
